---
title: "What is Data Analysis?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r include}
library(ggplot2)
```
# Inroduction

A data analysis will involve utilizing structured data to find tangible solutions with various programming languages for visualization and statistical work. Some of the programming languages used are R and SQL (server query language).

Typically, data analysis is used to understand structured data to gain insights into trends or actionable material.

## Analyzing a .csv file

We may begin here by loading a comma separated file (.csv) to gain insight about natural gas consumption in these United States. Typically, a cleaning of the data will involve removing any null values in the data-set before manipulation or any computation is undertaken.

The [data-set](https://www.eia.gov/dnav/ng/hist/n9140us2M.htm) we will utilize is for monthly consumption from January 2001 to August 2024 of Natural Gas.

```{r data}
my.data <- read.csv("./total_monthly_consumption.csv")
head(my.data)
```

## Loading a Plot

We shall embed a plot of our previously read .csv file for a visualization of U.S. Natural Gas Consumption and make an inference by parsing a whole year.

```{r gas-plot}
# Get Last Year
Months <- head(my.data$Month, 12)
Consumptions <- head(my.data$Consumption, 12)
# Create Proper Frame
annual.data <- head(my.data, 12)
# Parse Months as a Level, then Plot
ggplot(data = annual.data, aes(x = factor(Months, c("Aug-24", "Jul-24", "Jun-24", "May-24", "Apr-24", "Mar-24", "Feb-24", "Jan-24", "Dec-23", "Nov-23", "Oct-23", "Sep-23")), y = Consumptions, group = 1)) +
  geom_line() +
  geom_point() +
  labs(title = "Monthly Consumption",
       x = "Month",
       y = "Consumption") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5))
```

## Conclusion

Notice the oscillation of the graph near 'winter' months. It is safe to make an inference that U.S. Natural Gas monthly consumption increased drastically near winter to keep homes, businesses, and what have you warm during what appears to be cold months. This would be our 'inference' or 'insight' into the data through visualization.
