---
title: "What is Data Science?"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r include}
library(ggplot2)
```

# Introduction

Data science often utilizes techniques to make a prediction about the future. The field of data science makes use of the concept of predictive modeling. Often dealing with the unknown by using more advanced data techniques to make predictions about a data set.

Typically, data science is involved with the building of data sets or structuring an unstructured data set to make those predictive models.

## Reading and Parsing Data

As you may have seen from the previous page on 'what is analysis' we had to partly clean up our data. The file containing our [data-set](https://www.eia.gov/dnav/ng/hist/n9140us2M.htm) with consumption from January 2001 to August 2024 had a character vector instead of a date type. This column in the data frame had to be manipulated where it was readable by our graph we computed. Now, we will summarize the data with some basic statistical computation.

```{r data summary}
my.data <- read.csv("total_monthly_consumption.csv")
summary(my.data)
```

## Reading a Plot

```{r reading plot}
# Get Last Year
Months <- head(my.data$Month, 12)
Consumptions <- head(my.data$Consumption, 12)
# Create Proper Frame
annual.data <- head(my.data, 12)
# Parse Months as a Level, then Plot
ggplot(data = annual.data, aes(x = factor(Months, c("Aug-24", "Jul-24", "Jun-24", "May-24", "Apr-24", "Mar-24", "Feb-24", "Jan-24", "Dec-23", "Nov-23", "Oct-23", "Sep-23")), y = Consumptions, group = 1)) +
  geom_line() +
  geom_point() +
  labs(title = "Monthly Consumption",
       x = "Month",
       y = "Consumption") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5))
```

## Conclusion

The advanced part of making predictions is to extrapolate data for a future reference. We are using the same visual reference in the previous page on 'what is analysis', but we are making the assumption next year will have similar results for these United States regarding higher consumption during the months starting with October through March. We will also make the conjecture that peak consumption will happen in January around 3700000 million cubic feet.
